Classical probability measures as pullback of quantum probability measures?

### 2022-04-13 pullback.tex
pullback.lyx Update here and there...

defined by precomposition is a classical probability measure because

@@

 &  & \mu\left(\varphi(\Omega)\right)=\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
 &  & \mu\left(\varphi\left(\overline{E}\right)\right)=\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\

@@

and for each pair of disjoin $E_{0}$ and $E_{1}$: 

@@

\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\left(\mathbb{1}-\mathbb{1}\right)\right)\\

@@

Since that ``precomposition'' is called ``pullback'' in differential

@@

investigate.}, we will use their notation and write the precomposition $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)$

@@

Probability measure could be simplified as & probability mass function $m:\Omega\rightarrow[0,1]$ such that $\left(\varphi^{*}\mu\right)(E)=\sum_{\omega\in E}m(\omega)$ & mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$ & \tabularnewline

@@

 & Need a notation for $\varphi^{*}\mu\mapsto m$ to keep going & Need a notation for $\mu\mapsto\rho$ to keep going & We may draw commuting diagram (?) here\tabularnewline

@@

random variable, but summarize quantum measurement process as an observable.

@@

has a push forward observable. This is better in the sense that we
don't have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be
different for different orthonormal basis, but every theorem for IVPMs
starts from the quantum part with an observable, so we need the ambiguous
$\varphi^{*}\mathbf{O}$ for each different orthonormal basis anyway.} According to Gleason's theorem, the table could be extended to simplify

>>>>

defined by precomposition is a classical probability measure\footnote{\begin{proof}

@@

 &  & \mu\left(\varphi(\Omega)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
 &  & \mu\left(\varphi\left(\overline{E}\right)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\

@@

and for each pair of disjoint $E_{0}$ and $E_{1}$, we have 
\[
\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}\varphi\left(\emptyset\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mathbb{0}\,,
\]
i.e., $\varphi\left(E_{0}\right)$ and $\varphi\left(E_{1}\right)$
are orthogonal, and then: 

@@

\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)\right)\\

@@

\end{proof}}. Since that ``precomposition'' is called ``pullback'' in differential

@@

investigate.}, we will use their notation, write the precomposition $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)$

@@

Probability measure could be simplified as & probability mass function $m:\Omega\rightarrow[0,1]$ such that $\left(\varphi^{*}\mu\right)\left(E\right)=\sum_{\omega\in E}m\left(\omega\right)$ & mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$ & \tabularnewline

@@

 & Need a notation for $\varphi^{*}\mu\mapsto m$ to keep going & Need a notation for $\mu\mapsto\rho$ to keep going & We may draw commuting diagram here?\tabularnewline

@@

random variable, but summarize quantum measurement process as observable.

@@

has a push forward observable. This is better in a sense that we don't
have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be different
for different orthonormal bases, but every theorem for IVPMs starts
from the quantum part with an observable, so we need the notation
$\varphi^{*}\mathbf{O}$ and fixing an orthonormal basis to disambiguate
$\varphi^{*}\mathbf{O}$ anyway.} According to Gleason's theorem, the table could be extended to simplify
